---
title: "ETC5521 Assignment 1"
subtitle: "All about Coffee"
team: Hakea
author:
  - Siddhant V Tirodkar
  - Varsha Ujjinni Vijay Kumar
date: "`r Sys.Date()`"
output: 
  html_document
---

[This assignment is for ETC5521 Assignment 1 by Team `r rmarkdown::metadata$team` comprising of `r knitr::combine_words(rmarkdown::metadata$author)`.]{style="color:#006DAE;"}


# Introduction and motivation

Coffee is the most popular beverage in the whole world. Let's see, you're reading this with a cup of coffee,aren't you? 

So wouldn't it be interesting to know how the coffee you drink is graded to be either the best or bad coffee batches? The country with the best graded coffee beans and why are they considered the best, the different factors which elucidate the quality of the coffee cultivated. From where they come, the processing method to get them?


# Data description

*Source of data* : This data originally comes from Coffee Quality Institute website and was scraped by and used by  a github account by  [James DeLoux](https://github.com/jldbc/coffee-quality-database) ,this data was then re-posted on [Kaggle](https://www.kaggle.com/volpatto/coffee-quality-database-from-cqi?select=merged_data_cleaned.csv) . And this dataset was analysed by [Yorgos Askalidis](https://towardsdatascience.com/the-data-speak-ethiopia-has-the-best-coffee-91f88ed37e84).

*Collection Methods*: This dataset contains the review of 1312 arabica 28 robusta beans from the Coffee Quality Institute’s trained reviewers. 

*Time Frame of dataset*: January 2018

The original data is a dataframe was scraped by James LeDoux from the Coffee Quality Institute website which has a few missing values columns within it, so the author has cleaned the dataset by removing the variables:  “view_certificate_1”, “view_certificate_2”,etc.

Further the variable names within the arabica dataset was cleaned using the *clean_names()* function form the **janitor R package**, which helps remove any symbols within the name to give a clean format. And the robusta data was read with some column specifications and the same process of cleaning the variable names was used on the second dataset as well, and a few variable names were changed for the user’s better understanding and the literal meaning of each variable by using the *rename()* function: 
Acidity to salt_acid, sweetness to bitter_sweet, aroma to fragrance_aroma, etc.

Since both these datasets are just two different species of coffee , they were joined to produce the dataset which we now use “coffee_ratings.csv” with 1339 observations and 43 variables. 

```{r data, message=FALSE, warning=FALSE,include=FALSE}
# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")

tuesdata <- tidytuesdayR::tt_load('2020-07-07')
tuesdata <- tidytuesdayR::tt_load(2020, week = 28)

coffee_ratings <- tuesdata$coffee_ratings
```

Structure of data: 

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
glimpse(coffee_ratings) 
```

After this knowing what each of those variables define with respect to our topic is important so here are a few variables we should know the general meaning to in accordance with coffee:

- Aroma(aroma grade) : Has both fragrance(ground beans) and aroma (hot water with coffee powder) 

- Aftertaste : length of positive flavor remaining after the coffee is swallowed.

- Acidity : the score depends on the origin characteristics and other factors(degree of roast)

- Uniformity : refers to the consistency of flavor . 2 points are awarded for each cup displaying this attribute, with a maximum of 10 points if all 5 cups are the same.

- Clean_cup : refers to a lack of interfering negative impressions from first ingestion to final aftertaste, a "transparency" of cup.  2 points are awarded for each cup displaying the attribute.

- Cupper_points : The cupper marks the intensity of the Aroma on a scale. A final score for Fragrance and Aroma is now given on the basis of a combined evaluation of Fragrance and Aroma.

- Category 1 defect: Full black or sour bean, pod/cherry, and large or medium sticks or stones.


- Category 2 defect: Parchment, hull/husk, broken/chipped, insect damage, partial black or sour, shell, small sticks or stones, water damage.

- Quakers: Quakers are unripened beans that are hard to identify during hand sorting and green bean inspection.

QUestions :

- Which Country produces the best quality coffee beans?

- Does Altitude really affect the quality of the beans produced?

- Which countries perform best on individual grading criteria such as aroma, acidity, sweetness etc?

- Which regions/companies perform better than others in the quality of the coffee beans produced, intra-country?


# Explatory Data Analysis

Coffee beans are harvested, produced and exported throughout almost every country in the world. This dataset contains the data of ` r unique(coffee_ratings$country_of_origin)` leading manufactures of coffee. We will be focusing on the manufacturing and the quality aspect of the beans produced in this report. The two main variants of a coffee bean are Arabica and Robusta. Approximately 60% of coffee produced in the world is Arabica and approximately 40% is Robusta. Arabica beans consists about 0.8%-1.4% caffeine and Robusta beans  consists  of 1.7%-4% caffeine. Coffee is one of the most important cash crop in the world. [Wikipedia](https://en.wikipedia.org/wiki/Coffee_bean) 

## Best Quality Beans

So to address the primary question as **Which country produces best quality coffee beans?** as we can see in `r figr("best-country",TRUE,type = "Figure")` clearly most owners of top-20 best quality coffee beans produced are in Ethiopia followed by the United States. The **total_cup_points** is plotted on a pie-chart. The *total_cup_points** variable denotes the overall rating achieved by the coffee bean awarded by the Coffee Quality Institute's trained reviewers. This rating is a cumulative sum of 10 individual quality measures like aroma, flavour, aftertaste, acidity, body, balance, uniformity, clean cup, sweetness and cupper points. In the later section of this report we will also look at how the major countries perform individually on each of these criterias.
```{r best-country, anchor = "Figure", results='asis'}
## we;ll use the pie chart for this question i feel and a bar plot for the last one.
coun <- coffee_ratings %>% 
  select(total_cup_points,species,country_of_origin,owner) %>% 
  group_by(country_of_origin) %>% 
  arrange(desc(total_cup_points)) %>% 
  head(20)
#alternative to the above bar plot for best quality country
ggplot(coun, 
       aes(x= "", 
           y = total_cup_points, 
           fill = country_of_origin)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  scale_fill_brewer("blues")
```

## Altitude v/s Quality (# Have to write on this part but will need your help.)

Next, we will will probe into the next question **Does Altitude really affect the quality of the beans produced?** and to explore this we have fitted a linear model. **total_cup points** is the dependent variable and *altitude_mean_meters* as the independent variable. The fitted model returns a p-value of 0.646 and inspite a subtle upward slope being noticed the model cannot be considered statistically significant and this can be observed in figure . This can be explained due to the available data being of the best coffee beans produced around the world and most of the data has higher total_cup_points.

```{r}
 lm(total_cup_points ~ altitude_mean_meters, coffee_ratings) %>%   broom::tidy()
```

```{r}
ggplot(data = coffee_ratings, aes(x = total_cup_points, y = altitude_mean_meters)) +
  geom_point() +
  geom_smooth(method = lm)
```

```{r eval=FALSE, warning=FALSE, message=FALSE}
res <- cor.test(coffee_ratings$total_cup_points, as.numeric(coffee_ratings$altitude)) %>% broom::tidy()
res
```

```{r}
one.way <- aov(total_cup_points ~ processing_method , data = coffee_ratings)
summary(one.way) 
```

```{r}
plot(one.way, which = 1, col = c("blue"))
```


```{r}
factors <- lm(total_cup_points ~ aroma + flavor + aftertaste + acidity + body + balance + uniformity + clean_cup + sweetness + cupper_points + moisture, coffee_ratings) 
factors %>% broom::tidy()
```

```{r}
f <- broom::augment(factors)
ggplot(f, aes(x = .fitted, y = .resid)) + geom_point() + geom_smooth()
```

# Radar Plot

```{r}
coffee_ratings %>% filter(country_of_origin== c("Ethiopia","United States","Brazil", "Peru", "Indonesia")) %>% 
  select(aroma, flavor,aftertaste,acidity,body,balance,uniformity,clean_cup,sweetness,cupper_points, moisture, total_cup_points, country_of_origin) %>%  group_by(country_of_origin) %>% summarise(ma = mean(aroma), mfl= mean(flavor), maf = mean(aftertaste), mac = mean(acidity), mb = mean(body),mba = mean(balance),mu = mean(uniformity), mc = mean(clean_cup), ms = mean(sweetness), mcu = mean(cupper_points), mm = mean(moisture))
```

```{r}
library(fmsb)
data <- data.frame(aroma = c(10,0,7.89),
                   flavor = c(10,0,8.00),
                   aftertaste = c(10,0,7.89),
                   acidity = c(10,0,8.04),
                   body = c(10,0,7.92),
                   balance = c(10,0,7.97),
                   uniformtiy = c(10,0,9.87),
                   clean_cup = c(10,0,9.95),
                   sweetness = c(10,0,9.86),
                   cupper_points = c(10,0,8.04),
                   moisture = c(10,0,0.08))

Ethi <-radarchart(data, 
           seg = 10,
           title = "Ethiopia",
           pfcol = scales::alpha("purple", 0.3),
           plwd = 2)
```

```{r}
library(fmsb)
data <- data.frame(aroma = c(10,0,7.60),
                   flavor = c(10,0,7.54),
                   aftertaste = c(10,0,7.36),
                   acidity = c(10,0,7.46),
                   body = c(10,0,7.53),
                   balance = c(10,0,7.54),
                   uniformtiy = c(10,0,9.75),
                   clean_cup = c(10,0,9.69),
                   sweetness = c(10,0,9.93),
                   cupper_points = c(10,0,7.49),
                   moisture = c(10,0,0.08))

Brazil <- radarchart(data, 
           seg = 10,
           title = "Brazil",
           pfcol = scales::alpha("pink", 0.3),
           plwd = 2) 
```


```{r}
library(fmsb)
data <- data.frame(aroma = c(10,0,7.79),
                   flavor = c(10,0,7.87),
                   aftertaste = c(10,0,7.67),
                   acidity = c(10,0,7.87),
                   body = c(10,0,7.79),
                   balance = c(10,0,7.67),
                   uniformtiy = c(10,0,9.66),
                   clean_cup = c(10,0,9.66),
                   sweetness = c(10,0,8.71),
                   cupper_points = c(10,0,7.83),
                   moisture = c(10,0,0.00))

US <- radarchart(data, 
           seg = 10,
           title = "United States",
           pfcol = scales::alpha("skyblue", 0.3),
           plwd = 2) 
```


```{r}
library(fmsb)
data <- data.frame(aroma = c(10,0,7.44),
                   flavor = c(10,0,7.33),
                   aftertaste = c(10,0,7.22),
                   acidity = c(10,0,7.38),
                   body = c(10,0,7.53),
                   balance = c(10,0,7.44),
                   uniformtiy = c(10,0,9.77),
                   clean_cup = c(10,0,10.00),
                   sweetness = c(10,0,10.00),
                   cupper_points = c(10,0,8.14),
                   moisture = c(10,0,0.08))

Peru <- radarchart(data, 
           seg = 10,
           title = "Peru",
           pfcol = scales::alpha("tomato", 0.3),
           plwd = 2) 
```


```{r}
library(fmsb)
#library(ggradar)
dataI <- data.frame(aroma = c(10,0,7.68),
                   flavor = c(10,0,7.41),
                   aftertaste = c(10,0,7.20),
                   acidity = c(10,0,7.21),
                   body = c(10,0,7.60),
                   balance = c(10,0,7.23),
                   uniformtiy = c(10,0,9.86),
                   clean_cup = c(10,0,10.00),
                   sweetness = c(10,0,9.86),
                   cupper_points = c(10,0,7.26),
                   moisture = c(10,0,0.07))


Indo <- radarchart(data,
           seg = 10,
           title = "Indonesia",
           pfcol = scales::alpha("gold", 0.3),
           plwd = 2)
```

## Leading Regions

To respond to our final question **Which regions/companies perform better than others in the quality of the coffee beans produced, intra-country?** we use a barplot in figure 9. The x-axis shows the total points a coffe bean recieves and the y-axis depicts the different regions where they were produced. The bars are coloured according to the country they belong to. Evidently Hulia is a region in Colombia where coffee beans get consistent good ratings and is the best region to grow coffee beans.

```{r regions, message=FALSE,warning=FALSE}
reg <- coffee_ratings %>% 
  group_by(country_of_origin,species,region,total_cup_points) %>% 
  summarise(sum = sum(total_cup_points)) %>% 
  arrange(desc(sum)) %>% 
  head(40)

ggplot(reg,
        aes(x = reorder(region, -total_cup_points),
            y = total_cup_points,
            fill = country_of_origin)) + 
geom_col()
```

## Largest Producer

We also observe that Colombia is the largest producer of coffee beans Arabica variant with more than 40000 bags followed by Guatemala and Brazil. We establish using a bar-plot in figure 4 with y-axis representing the number of bags produced and x-axis representing different countries. The Figure shows the top-6 coffee bean producing countries.

```{r}
# highest producer using bags
highest_produce <- coffee_ratings %>% group_by(country_of_origin,species) %>% summarise(nob = sum(number_of_bags)) %>% arrange(desc(nob)) %>% head()

ggplot(highest_produce, 
       aes(x = reorder(country_of_origin, - nob), 
           y = nob)) + 
  geom_col(fill = "deepskyblue4") +
  geom_text(label =  highest_produce$species)
```

# References

- The dataset was taken from (https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-07-07/readme.md)

- Further inferences were drawn into the data taking help from (https://database.coffeeinstitute.org/coffee/357789/grade)

