---
title: "ETC5521 Assignment 2"
subtitle: "All about Coffee"
team: Hakea
author:
  - Dang Thanh Nguyen
  - Rui Min Lin
date: "`r Sys.Date()`"
output: 
  bookdown::html_document2: 
    citation_package: biblatex
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
bibliography: ref.bib
biblio-style: authoryear-comp
link-citations: yes
   

---

[This assignment is for ETC5521 Assignment 1 by Team `r rmarkdown::metadata$team` comprising of `r knitr::combine_words(rmarkdown::metadata$author)`.]{style="color:#006DAE;"}


# Introduction and motivation

Coffee is the most popular beverage in the whole world, as an everyday beverage people are attracted not only by its taste, but also the continuous refreshing effect that helps people stay focused. Let's see, you're reading this with a cup of coffee, aren't you? 

So wouldn't it be interesting to know how the coffee you drink is graded to be either the best or bad coffee batches? The country with the best graded coffee beans and why are they considered the best, the different factors which elucidate the quality of the coffee cultivated. From where they come, the processing method to get them?


# Data description

*Source of data* : This data originally comes from Coffee Quality Institute website and was scraped by and used by  a github account by  [James DeLoux](https://github.com/jldbc/coffee-quality-database) ,this data was then re-posted on [Kaggle](https://www.kaggle.com/volpatto/coffee-quality-database-from-cqi?select=merged_data_cleaned.csv) . And this dataset was analysed by [Yorgos Askalidis](https://towardsdatascience.com/the-data-speak-ethiopia-has-the-best-coffee-91f88ed37e84).

*Collection Methods*: This dataset contains the review of 1312 arabica and 28 robusta beans from the Coffee Quality Institute’s trained reviewers. 

*Time Frame of dataset*: January, 2018

The original data is a dataframe scraped by James LeDoux from the Coffee Quality Institute website which has a few missing values columns within it, so the author has cleaned the dataset by removing the variables:  “view_certificate_1”, “view_certificate_2”,etc.


Since both the datasets (Arabica and Robusta) are just two different species of coffee , they were joined to produce the dataset, which we now use “coffee_ratings.csv” with 1339 observations and 43 variables. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(fmsb)
library(kfigr)
library(gridExtra)
library(bookdown)
```

```{r data, message=FALSE, warning=FALSE,include=FALSE}
# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")

tuesdata <- tidytuesdayR::tt_load('2020-07-07')
tuesdata <- tidytuesdayR::tt_load(2020, week = 28)

coffee_ratings <- tuesdata$coffee_ratings

```

```{r alternative, eval=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
# If the above code renders an error, alternatively this chunk can be used to read the data!
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')
```

```{r data-clean}
# Tidy the name a bit

coffee_ratings_clean <- coffee_ratings %>% 
  # Shorten the variables name
  rename(country = country_of_origin,
         total_points = total_cup_points,
         method = processing_method) %>%
  mutate(country = if_else(country == "Tanzania, United Republic Of", "Tanzania", country)) %>%
  # Shorten the name of obs
  mutate(country = recode(country, 
                          "United States" = "US",
                          "United States (Hawaii)" = "US (Hawaii)",
                          "United States (Puerto Rico)" = "US (Puerto Rico)"
                          ))

ggplot(coffee_clean, aes(total_points, country))+
  geom_point()
# There is an outlier in total cup points


# There is a NA in country name
# I (Thomas) performed a quick check, and it is from colombia (based on the producer)
# So I changed it

coffee_clean <- coffee_clean %>%
  mutate(country = replace(country, is.na(country), "Colombia"))

```


**Structure of data:** 

After this knowing what each of those variables define with respect to our topic is important so here are a few variables we should know the general meaning to in accordance with coffee:

- *Aroma(aroma grade)* : Has both fragrance (ground beans) and aroma (hot water with coffee powder) 

- *Aftertaste* : length of positive flavor remaining after the coffee is swallowed.

- *Acidity* : the score depends on the origin characteristics and other factors(degree of roast)

- *Uniformity* : refers to the consistency of flavor . 2 points are awarded for each cup displaying this attribute, with a maximum of 10 points if all 5 cups are the same.

- *Clean_cup* : refers to a lack of interfering negative impressions from first ingestion to final aftertaste, a "transparency" of cup.  2 points are awarded for each cup displaying the attribute.

- *Cupper-points* : The cupper marks the intensity of the Aroma on a scale. A final score for Fragrance and Aroma is now given on the basis of a combined evaluation of Fragrance and Aroma.

- *Category 1 defect*: Full black or sour bean, pod/cherry, and large or medium sticks or stones.

- *Category 2 defect*: Parchment, hull/husk, broken/chipped, insect damage, partial black or sour, shell, small sticks or stones, water damage.

- *Quakers*: Quakers are unripened beans that are hard to identify during hand sorting and green bean inspection.

**Questions of interest**

The aim of this report is to discover characteristics within best-graded coffee bean countries, and will examine from different aspects of coffee beans to explore the likely factors that influence its quality and taste.

Secondary question:

1. Which Country produces the best quality coffee beans?

2. Does Altitude really affect the quality of the beans produced?

3. Which countries perform best on individual grading criteria such as aroma, acidity, sweetness etc?

4. Which regions/companies perform better than others in the quality of the coffee beans produced, intra-country?

5. Compare the characteristics of Arabica and Robusta, what insights can be discovered?

6. Are there any similarities in the processing method of coffee beans amongst the best-graded coffee beans countries?

# Explatory Data Analysis

Coffee beans are harvested, produced and exported throughout almost every country in the world. This dataset contains the data of `r unique(coffee_ratings$country_of_origin)`. We will be focusing on the manufacturing and the quality aspect of the beans produced in this report. The two main variants of a coffee bean are Arabica and Robusta. Approximately 60% of coffee produced in the world is Arabica and approximately 40% is Robusta. Arabica beans consists about 0.8%-1.4% caffeine and Robusta beans  consists  of 1.7%-4% caffeine. Coffee is one of the most important cash crop in the world. [Wikipedia](https://en.wikipedia.org/wiki/Coffee_bean) 

## Best Quality Beans

So to address the primary question as **Which country produces best quality coffee beans?** as we can see in `r figr("best-country",TRUE,type = "Figure")` clearly most owners of top-20 best quality coffee beans produced are in Ethiopia followed by the United States. The **total_cup_points** is plotted on a pie-chart. The *total_cup_points* variable denotes the overall rating achieved by the coffee bean awarded by the Coffee Quality Institute's trained reviewers. This rating is a cumulative sum of 10 individual quality measures like aroma, flavour, aftertaste, acidity, body, balance, uniformity, clean cup, sweetness and cupper points. In the later section of this report we will also look at how the major countries perform individually on each of these criterias.

```{r q1, results='asis', fig.cap="Best country quality-wise"}
# Get countries that have more then 5 beans graded
temp <- coffee_clean %>% group_by(country) %>%
  summarise(count = n()) %>% 
  filter(count > 5) %>% 
  ungroup() %>% 
  pull(country) # Get the country name out as vector)
coffee_clean %>% filter (country %in% temp) %>%
mutate(country = fct_reorder(country, total_points)) %>% 
ggplot(aes(x = total_points,
           y = country))+
  geom_boxplot()
```
## Altitude v/s Quality 

Next, we will will probe into the next question **Does Altitude really affect the quality of the beans produced?** and to explore this we have fitted a linear model. **total_cup points** is the dependent variable and **altitude_mean_meters** as the independent variable. We have considered only the top 1105 observations for constructing the model because 3 extreme values and missing values were rendering a statistically insignificant model with a p-value of more than 0.9. The fitted model returns a p-value of 0.0003 which suggests that the model is statistically significant. `r figr("alt-plot",TRUE,type = "Figure")`  shows a positive relationship between altitude and quality of coffee beans produced. Altitude plays an important role in the formation of acidity and bitterness and enhances coffee quality attributes.

```{r altitude, echo=FALSE}
alt_data <- coffee_ratings %>% arrange(altitude_mean_meters) %>% head(1105)

```

```{r alt-lrm, message=FALSE,warning=FALSE, echo=FALSE}
 lm(total_cup_points ~ altitude_mean_meters, alt_data) %>%   broom::tidy() %>% kable(caption = "Altitude v/s Quality stats") %>% kable_styling()
```

```{r alt-plot, anchor = "Figure", results='asis', fig.cap="Regression model for Altitude", echo=FALSE,warning=FALSE,message=FALSE}
ggplot(data = alt_data, aes(x = total_cup_points, y = altitude_mean_meters)) +
  geom_point() +
  geom_smooth(method = lm)
```

```{r cor-test, eval=FALSE, warning=FALSE, message=FALSE,echo=FALSE}
#alternate verification for altitude
res <- cor.test(coffee_ratings$total_cup_points, as.numeric(coffee_ratings$altitude)) %>% broom::tidy()
res
```

## Processing Method v/s Quality

To check if the processing method affects the quality of coffee beans produced, we have taken help of the ANOVA test as the processing method is a categorical variable. The ANOVA test returns p-values very far away from the confidence interval of 5% which can be observed when we plot the residuals against the fitted values in `r figr("one-way",TRUE,type = "Figure")` . Hence it is established that the processing methods used in producing the coffee beans does not influence the quality of beans produced.


```{r method-aov,echo=FALSE}
one.way <- aov(total_cup_points ~ processing_method , data = coffee_ratings)
summary(one.way) 
```

```{r one-way,anchor = "Figure", results='asis',fig.cap="ANOVA test for processing methods vs Quality",echo=FALSE}
plot(one.way, which = 1, col = c("blue"))
```

## Defects v/s Quality

After the linear model for altitude turned out to be insignificant, we figured there are several other variables in the dataset that we could try fitting a model. The dataset contains category one and category two defects which are also known as primary and secondary defects and we fitted a muti-variate model using the same. The model after considering both the variables return a p-value very close to 0 and hence this model is considered a good one and as can be seen in `r figr("def-plot",TRUE,type = "Figure")` which suggest that almost all the residuals reside very close to the 0 line with a very few outliers. Thus it can be understood that defects influence the quality of coffee beans produced.

```{r def-lrm, warning=FALSE,message=FALSE,echo=FALSE}
defects <- lm(total_cup_points ~ category_one_defects + category_two_defects, coffee_ratings) 
defects %>%  broom::tidy() %>% kable(caption = "Defects linear regression model") %>% kable_styling()
```

```{r def-plot, anchor = "Figure", results='asis',echo=FALSE,warning=FALSE,message=FALSE}
d <- defects %>% broom::augment()
ggplot(d, aes(x = .fitted, y = .resid)) + geom_point() + geom_smooth()
```

## Individual Criteria 

To check which criteria the top 5 countries perform best in we have used radar charts from `r figr("Eth-radar",TRUE,type = "Figure")` onwards. A radar chart is a useful way to depict multi-variate observations. Each criteria is rated out of a total 10 points and all the 10 criteria are plotted together on the radar chart along with moisture percentage to understand how a particular country performs on individual criteria. The top-5 coffee bean producing countries according to our analysis are Ethiopia, Brazil, United States, Indonesia and Peru.


```{r mean,message=FALSE,warning=FALSE,echo=FALSE}
coffee_ratings %>% filter(country_of_origin== c("Ethiopia","United States","Brazil", "Peru", "Indonesia")) %>% 
  select(aroma, flavor,aftertaste,acidity,body,balance,uniformity,clean_cup,sweetness,cupper_points, moisture, total_cup_points, country_of_origin) %>%  group_by(country_of_origin) %>% summarise(ma = mean(aroma), mfl= mean(flavor), maf = mean(aftertaste), mac = mean(acidity), mb = mean(body),mba = mean(balance),mu = mean(uniformity), mc = mean(clean_cup), ms = mean(sweetness), mcu = mean(cupper_points), mm = mean(moisture)) %>% kable(caption = "Means for different Individual grading criterias") %>% kable_styling()
```

```{r Eth-radar,anchor = "Figure", results='asis',echo=FALSE}
dataE <- data.frame(aroma = c(10,0,7.89),
                   flavor = c(10,0,8.00),
                   aftertaste = c(10,0,7.89),
                   acidity = c(10,0,8.04),
                   body = c(10,0,7.92),
                   balance = c(10,0,7.97),
                   uniformtiy = c(10,0,9.87),
                   clean_cup = c(10,0,9.95),
                   sweetness = c(10,0,9.86),
                   cupper_points = c(10,0,8.04))

Ethi <- radarchart(dataE, 
           seg = 10,
           title = "Ethiopia",
           pfcol = scales::alpha("purple", 0.3),
           plwd = 2)
```

```{r us-radar,echo=FALSE}
dataU <- data.frame(aroma = c(10,0,7.79),
                   flavor = c(10,0,7.87),
                   aftertaste = c(10,0,7.67),
                   acidity = c(10,0,7.87),
                   body = c(10,0,7.79),
                   balance = c(10,0,7.67),
                   uniformtiy = c(10,0,9.66),
                   clean_cup = c(10,0,9.66),
                   sweetness = c(10,0,8.71),
                   cupper_points = c(10,0,7.83))

US <- radarchart(dataU, 
           seg = 10,
           title = "United States",
           pfcol = scales::alpha("skyblue", 0.3),
           plwd = 2) 
```


```{r brazil-radar,echo=FALSE}
dataB <- data.frame(aroma = c(10,0,7.60),
                   flavor = c(10,0,7.54),
                   aftertaste = c(10,0,7.36),
                   acidity = c(10,0,7.46),
                   body = c(10,0,7.53),
                   balance = c(10,0,7.54),
                   uniformtiy = c(10,0,9.75),
                   clean_cup = c(10,0,9.69),
                   sweetness = c(10,0,9.93),
                   cupper_points = c(10,0,7.49))

Brazil <- radarchart(dataB, 
           seg = 10,
           title = "Brazil",
           pfcol = scales::alpha("pink", 0.3),
           plwd = 2) 
```


```{r peru-radar,echo=FALSE}
dataP <- data.frame(aroma = c(10,0,7.44),
                   flavor = c(10,0,7.33),
                   aftertaste = c(10,0,7.22),
                   acidity = c(10,0,7.38),
                   body = c(10,0,7.53),
                   balance = c(10,0,7.44),
                   uniformtiy = c(10,0,9.77),
                   clean_cup = c(10,0,10.00),
                   sweetness = c(10,0,10.00),
                   cupper_points = c(10,0,8.14))

Peru <- radarchart(dataP, 
           seg = 10,
           title = "Peru",
           pfcol = scales::alpha("tomato", 0.3),
           plwd = 2) 
```


```{r indo-radar,anchor = "Figure", results='asis',echo=FALSE}
dataI <- data.frame(aroma = c(10,0,7.68),
                   flavor = c(10,0,7.41),
                   aftertaste = c(10,0,7.20),
                   acidity = c(10,0,7.21),
                   body = c(10,0,7.60),
                   balance = c(10,0,7.23),
                   uniformtiy = c(10,0,9.86),
                   clean_cup = c(10,0,10.00),
                   sweetness = c(10,0,9.86),
                   cupper_points = c(10,0,7.26))


Indo <- radarchart(dataI,
           seg = 10,
           title = "Indonesia",
           pfcol = scales::alpha("gold", 0.3),
           plwd = 2)
```

```{r merged}
grid.arrange(Ehi, US, Brazil, Peru, Indo, ncol = 2)
```

After looking at these plots, the conclusion drawn are as follows: The common characteristics that these top 5 countries have are the consistent higher values of *uniformity* and *clean cup*. Among all these countries, it can be seen that the country **Ethiopia** has the highest values for all the different characteristics that we have proven to have a significant affect on the quality of the coffee beans in the above sections. It is also interesting how the *sweetness* has a perfect score of 10 in all other countries other than *United States* as depicted.


## Leading Regions

To respond to our final question **Which regions/companies perform better than others in the quality of the coffee beans produced, intra-country?** we use a barplot in `r figr("regions",TRUE,type = "Figure")`. The x-axis shows the total points a coffe bean recieves and the y-axis depicts the different regions where they were produced. The bars are coloured according to the country they belong to. Evidently Hulia is a region in Colombia where coffee beans get consistent good ratings and is the best region to grow coffee beans.

```{r regions, anchor = "Figure", results='asis', message=FALSE,warning=FALSE, fig.cap="Best Regions for the quality of coffee beans",echo=FALSE}
reg <- coffee_ratings %>% 
  group_by(country_of_origin,species,region,total_cup_points) %>% 
  summarise(sum = sum(total_cup_points)) %>% 
  arrange(desc(sum)) %>% 
  head(40)

ggplot(reg,
        aes(x = reorder(region, -total_cup_points),
            y = total_cup_points,
            fill = country_of_origin)) + 
  xlab("Region")+
geom_col()
```

## Largest Producer

We also observe that Colombia is the largest producer of coffee beans Arabica variant with more than 40000 bags followed by Guatemala and Brazil. We establish using a bar-plot in `r figr("producer",TRUE,type = "Figure")` with y-axis representing the number of bags produced and x-axis representing different countries. The Figure shows the top-6 coffee bean producing countries.

```{r producer, anchor = "Figure", results='asis', message=FALSE, warning=FALSE, fig.cap="Largest producer country-wise",echo=FALSE}
highest_produce <- coffee_ratings %>% group_by(country_of_origin,species) %>% summarise(nob = sum(number_of_bags)) %>% arrange(desc(nob)) %>% head()

ggplot(highest_produce, 
       aes(x = reorder(country_of_origin, - nob), 
           y = nob)) + 
  geom_col(fill = "deepskyblue4") +
  labs(x = "Country", y = "Number of bags produced") +
  geom_text(label =  highest_produce$species)
```

# References

- The dataset was taken from (https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-07-07/readme.md)

- Further inferences were drawn into the data taking help from (https://database.coffeeinstitute.org/coffee/357789/grade)

- Cerda, R., Allinne, C., Gary, C., Tixier, P., Harvey, C. A., Krolczyk, L., ... & Avelino, J. (2017). Effects of shade, altitude and management on multiple ecosystem services in coffee agroecosystems. European Journal of Agronomy, 82, 308-319.

- The data is in: Ethiopia has the best coffee. (2020). Retrieved 27 August 2020, from https://towardsdatascience.com/the-data-speak-ethiopia-has-the-best-coffee-91f88ed37e84

- En.wikipedia.org. 2020. Coffee Bean. [online] Available at: <https://en.wikipedia.org/wiki/Coffee_bean> [Accessed 27 August 2020].
